Propositions as Sessions, Mechanically

### 2015-04-12 paper/formalisation.tex
Sketched some discussion of cut elimination progress.

Unfortunately, the theorem has eluded attempts at mechanised proof so far. The
hypothesis of a well-typed process \coqe$P$ is not sufficient to prove the
theorem. For instance, the \coqe$cp_cut$ constructor does not ensure that
there is a duality relationship between the subprocesses. Following informal
proofs, it is likely to require a termination measure involving the length of
the derivation is needed. Additionally, the locally nameless representation
creates subgoals for which it is not clear how to prove. For instance, a
commuting conversion is only defined if the logical operator corresponds to a
free variable but induction on \key{WT} yields two cases one of which applies
the logical operator to the top-level cut variable. Since there is no
relationship between the subprocesses, in general it will not be possible to
apply a principal cut rule.

>>>>

Unfortunately, the theorem has eluded attempts at mechanised proof so far. The
hypothesis of a well-typed process \coqe$P$ is not sufficient to prove the
theorem. For instance, the \coqe$cp_cut$ constructor does not ensure that
there is a duality relationship between the subprocesses. Following informal
proofs, it initially seemed likely that the proof required a termination
measure involving the length of the derivation. However due to the
difficulties in trying to prove the above rule some doubt was
seeded. additionally previous attempts in the literature formalised cut
elimination using a deep embedding perhaps an alternative formulation of the
reduction relation as a deep embedding expressed using derivations would
permit progress on the proof but this particular avenue is left for future
work

Formalised efforts for proving cut elimination for other logics have adopted a
deep embedding~\cite{??,??,??}, where sequents and derivations are represented
explicitly rather than just the conclusion as in the shallow embedding adopted
here. It is unclear whether the cut elimination theorem can be rescued in the
current setting or not, but previous work suggests it is better to use other
approaches. It is worth noting that \citeauthor{Tews:2013}'s Coq development
significant; about 36,000 lines.

the locally nameless
representation creates subgoals for which it is not clear how to prove. For
instance, a commuting conversion is only defined if the logical operator
corresponds to a free variable, but induction on \key{WT} yields two cases one
of which applies the logical operator to the top-level cut variable and since
there is no relationship between the subprocesses, in general it will not be
possible to apply a principal cut rule.
